Physics-based protein structure prediction and design using the confinement method

### 2013-01-11 Paper/paper.tex

So far we have seen that the method is good at predicting preferences when the structures are not
very close to each other, how far from native can we go? In this section we want to explore what
happens when we use the method to describe low quality models. We use one of the CASP targets (pdb
id = 2KJX, CASP id = T0531) .
We mentioned earlier that our predictive abilities are greatly decreased with low model qualities. It is
better to have at least one good model to pick out the native/native like structures from the rest of the decoy. 
In order to test this hypothesis we performed another test with target T0531 of CASP9, in which we compared the crystal 
structure to five models from the MUFOLD server. The pdb id of this extracellular domain of the jumping translocation 
breakpoint protein is 2KJX and the CASP target code is T0531.
Looking at Figure~\ref{fig:T0531} shows: 1.) native is correctly
identified as expected and 2.) Surprisingly there is a high level of correlation between the GDT
ranking and the free energy ranking, only two structures with GDT\_TS score less than  35  are ordered
incorrectly. It is worth to note that models 2 and 3 have the same GDT and very different free
energies, meaning that the actual ordering could change a lot \cite{Perez2012}.

>>>>

So far we have seen that the method is good at predicting preferences when the structures are not
very close to each other, how far from native can we go? In this section we want to explore what
happens when we use the method to describe low quality models. We use one of the CASP targets (pdb
id = 2KJX, CASP id = T0531) .
We mentioned earlier that our predictive abilities are greatly decreased with low model qualities. It is
better to have at least one good model to pick out the native/native like structures from the rest of the decoy. 
In order to test this hypothesis we performed another test with target T0531 of CASP9, in which we compared the crystal 
structure to five models from the MUFOLD server. Pdb id of this extracellular domain of the jumping translocation 
breakpoint protein is 2KJX and CASP target code is T0531.
Looking at Figure~\ref{fig:T0531} shows: 1.) native is correctly
identified as expected and 2.) Surprisingly there is a high level of correlation between the GDT
ranking and the free energy ranking for model 1 and model 3, the rest three structures with GDT\_TS score less than  35  are ordered
incorrectly. It is worth to note that models 2 and 3 have the same GDT and very different free
energies, meaning that the actual ordering could change a lot \cite{Perez2012}. It is encouraging that at least
the method can pick out the best model with low GDT score of 44.
